Cartographie

### 2025-08-29 rapport/annexes.qmd
Fix liquid

---
title: "Annexes 2 : figures"

table-of-contents: true
toc-depth: 5         # profondeur max (#, ##) –‑ optionnel*
toc-title: "Sommaire" 
number-sections: true

@@

>>>>

---
title: "Cartographie"
render_with_liquid: false
table-of-contents: true
toc-depth: 5         # profondeur max (#, ##) –‑ optionnel*
toc-title: "Sommaire" 
number-sections: true

@@

```{python}
build_table(
    stats   = "stats",
    col     = "numday",
    echelle = "horaire",
    sat     = "sat_99.9",
    seasons = ["hydro"]
)
